### 2021-03-19 README.Rmd
add a link

- [seed dispersal paper](https://javirudolph.github.io/aracari/paper/paper.html) and the [figures](https://javirudolph.github.io/aracari/paper/figures_tables.html)
- [animal movement paper](https://javirudolph.github.io/aracari/movement_paper/rudolph_ch2.html)  
- [distributions paper](https://javirudolph.github.io/aracari/distributions_paper/rudolph_distributions.html)

>>>>

- [seed dispersal paper](https://javirudolph.github.io/aracari/paper/paper.html) and the [figures](https://javirudolph.github.io/aracari/paper/figures_tables.html)
- [animal movement paper](https://javirudolph.github.io/aracari/movement_paper/rudolph_ch2.html)  
- [distributions paper](https://javirudolph.github.io/aracari/distributions_paper/rudolph_distributions.html)
  - [info on the data](https://javirudolph.github.io/aracari/distributions_paper/format_raw_dat.html)
